Taming of Chance

========================================================
*Joel Willers*
*Jessica Short*
*Sen Zhou*
*Junzhao Hu*

It was a dark day at the ACME widget factory. A suspicious character was lurking in the corner of the huge manufacturing floor. Unknown to the employees, the stranger was ready to ruin their recent batch of widgets.

Sneaking between the giant machines towering like pillars of creation, the man made an

```{r}
#Joel
```
```{r}
#Jessica
library(ggplot2)
sc_u<-data.frame(rep(3,1000))
sc_n<-data.frame(rnorm(10000,3,.001))
sc<-cbind(sc_u,sc_n)
colnames(sc)<-c('uni','nrm')
sc_plot<-ggplot(sc, aes(nrm) ) +  geom_density(alpha = 0.2) 
sc_plot<-sc_plot+geom_bar(aes(x=uni))

```
'BOB!' yelled Mr. X, the manager of the plant. 'Last weeks, the screws were measured for our widgets and some were less than 2.5 inches!!'
Bob Replied: 'I'm sorry sir, we do quality control every night - I have workers measuring the screws on all the shifts'
Mr. X insisted that Bob stay all night counting screws. In his mind, all of the screws leaving his factory should measure 3 inches. How else could he maintain quality?

Little did he know, that there was a normal distribution working behind the scenes, undiscovered, moderating
```{r}
#Sen
```
```{r}
#Junzhao
```
You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

